---
title:  "<font color=#005CE6> R Crawler Crash Course </font>"
subtitle: <font color="green">Week 1</font>
author: 
    name: "Chih-Ping Chao, Chia-Chi Chang"
    affiliation: <font color=#22dbea>木刻思股份有限公司</font>
    email: "course@agilearning.io, george@data-sci.info"
    website: "http://agilearning.io, https://github.com/whizzalan"
date: "December 18, 2015"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
options(width=120)
# library(RColorBrewer)
# library(wordcloud)
# library(ggplot2)
library(data.table)
library(magrittr)
library(parallel)
library(stringr)
library(rvest)
library(httr)
# rmarkdown::render("index.Rmd")
```

## Hello ^R(Studio)?$

```{r RStudio}
grep("^R(Studio)?$", c("R","RStudio","Studio","R!", "abcR","RS","RStu","RStudioStudio"), value = TRUE)
```

## R Basic Syntax 

### Install packages

```{r install, eval = FALSE}
## install packages
packages_w1 <- c("rvest","stringr","selectr","quantmod","devtools","rjson","jsonlite","rlist","magrittr","pipeR")
install.packages(packages_w1)
## load package
library(magrittr)
library(rvest)
library(httr)
library(devtools)
## load all
sapply(packages_w1,library,character.only=TRUE)
```

### Useful functions to know data profile

```{r view data}
## View Data
head(iris)
tail(iris)
# View(iris)
summary(iris)

## explor object
attributes(iris)
str(iris)
class(iris)

## data shape
dim(iris)
ncol(iris)
nrow(iris)

```

### [DEMO] How to get string variable ?

```{r demo view data, eval=FALSE}
# install.packages("quantmod")
library(quantmod)

# quantmod::getSymbols 
getSymbols("2330.TW")
## What's wrong? ##
View(2330.TW)
View(getSymbols("2330.TW"))
TW_2330 <- getSymbols("2330.TW")

# get("2330.TW")

head(TW_2330)
tail(TW_2330)
View(TW_2330)
summary(TW_2330)

dim(TW_2330)
ncol(TW_2330)
nrow(TW_2330)
```

### Assign string variable

```{r Assign, eval=FALSE}
a <- 1:4
assign("a[1]", 2)
a[1] == 2          # FALSE
get("a[1]") == 2   # TRUE
```

### Setting env

```{r knew env}
head(ls())
getwd()
# setwd("~/works/RCrawler/RCrawlerCrashCourse")

# quantmod::
# quantmod:::

source("install_packages.r")
packages_w2

```

### Controller & function

```{r RCourse Fake,eval=FALSE}
RCourseDate <- c("2015-12-18","2016-01-04","2016-01-13","2016-01-29")
Today <- Sys.Date()
ifelse(Today %in% RCourseDate,"開薰學R語言","今日打東東")
```

```{r RCourse Real,echo=FALSE}
RCourseDate <- c("2015-12-18","2016-01-04","2016-01-13","2016-01-29")
Today <- RCourseDate[1]
ifelse(Today %in% RCourseDate,"開薰學R語言","今日打東東")
```

```{r do.call}
NormalSampleData <- function(N,mu){rnorm(N)+ mu}
system.time(for(i in 1:1e5) NormalSampleData(100,0))
system.time(for(i in 1:1e5) do.call(NormalSampleData, list(100,0)))

```

## [DEMO] Connector & Parser

### GET

```{r GET, eval = FALSE}

```

### POST Method

```{r POST, eval = FALSE}
## Syntax 1
httr::POST(URL, body= list(para1=paraVal1,para2=paraVal2))
## Syntax 2
httr::POST(URL, body= "para1=paraVal1_encode&para2=paraVal2_encode")
## Syntax 3
httr::POST(URL, body= "para1=paraVal1_encode&para2=paraVal2_encode", encode="form")
```

### [Appendix] magrittr

Pipe argument to right-hand side with `%>%`

- x `%>%` f is equivalent to f(x)
- x `%>%` f(y) is equivalent to f(x, y)
- x `%>%` f %>% g %>% h is equivalent to h(g(f(x)))
- x `%>%` f(y, .) is equivalent to f(y, x)
- x `%>%` f(y, z = .) is equivalent to f(y, z = x)

1. Yahoo Stock <http://tw.stock.yahoo.com/d/s/major_2451.html>

```{r Yahoo Stock}
library(httr)
library(rvest)

## Connector
Target_URL = "http://tw.stock.yahoo.com/d/s/major_2451.html"
res <- GET(Target_URL)
doc_str <- content(res, type = "text", encoding = "big5")

## Parser
if (.Platform$OS.type == "windows"){
  Sys.setlocale(category='LC_ALL', locale='C')
  data_table <- doc_str %>% read_html(encoding = "big-5") %>% html_nodes(xpath = "//table[1]//table[2]") %>% html_table(header=TRUE)
  Sys.setlocale(category='LC_ALL', locale='cht')
  data_table <- apply(data_table[[1]],2,function(x) iconv(x,from = "utf8"))
  colnames(data_table) <- iconv(colnames(data_table), from = "utf8")
}  else{
  data_table <- doc_str %>% read_html(encoding = "big-5") %>% html_nodes(xpath = "//table[1]//table[2]") %>% html_table(header=TRUE)
  data_table <- data_table[[1]]
}

# View(data_table)
```

2. 公開資訊觀測站 <http://mops.twse.com.tw/mops/web/t51sb01>

```{r mops}
library(httr)
library(rvest)
## Connector
res <- POST("http://mops.twse.com.tw/mops/web/ajax_t51sb01",body = "encodeURIComponent=1&step=1&firstin=1&TYPEK=sii&code=")
doc_str <- content(res, "text", encoding = "utf8")
write(doc_str, file = "mops.html")

## Parser
if (.Platform$OS.type == "windows"){
  Sys.setlocale(category='LC_ALL', locale='C')
  data_table <- doc_str %>% read_html(encoding = "big-5") %>% html_nodes(xpath = "//table[2]") %>% html_table(header=TRUE)
  Sys.setlocale(category='LC_ALL', locale='cht')
  data_table <- apply(data_table[[1]],2,function(x) iconv(x,from = "utf8"))
  colnames(data_table) <- iconv(colnames(data_table), from = "utf8")
}  else{
  data_table <- doc_str %>% read_html(encoding = "big-5") %>% html_nodes(xpath = "//table[2]") %>% html_table(header=TRUE)
  data_table <- data_table[[1]]
}

# View(data_table)
```

3. 銀行局 <http://goo.gl/88rBJz>

```{r bank, eval=FALSE}
library(rvest)
library(httr)
bankingUrl <- "http://www.banking.gov.tw/ch/home.jsp?id=192&parentpath=0,4&mcustomize=multimessage_view.jsp&dataserno=21207&aplistdn=ou=disclosure,ou=multisite,ou=chinese,ou=ap_root,o=fsc,c=tw&toolsflag=Y&dtable=Disclosure"

res <- GET(bankingUrl,set_cookies("cookiesession1=0F51E397POLJ4NQTC2CT7TGE8VBT033D; JSESSIONID=13A259B7048E0A96163333DA9D9BE428; fontsize=80%; _ga=GA1.3.807240144.1448956489; _gat=1"))
doc_str <- content(res, type = "text", encoding = "utf8")

# parser with URL
html <- read_html(doc_str)
monthsUrl <- html_nodes(html,"table[summary='信用卡重要業務及財務資訊揭露'] a[href]")

# get value 
html_text(monthsUrl)
html_attr(monthsUrl, name = "href")

# pipe to url
monthsUrlList <- content(res, type = "text", encoding = "utf8") %>% read_html %>% html_nodes("table[summary='信用卡重要業務及財務資訊揭露'] a") %>% html_attr("href")
monthsUrlList <- ifelse(substr(monthsUrlList,1,1)=='/',paste0("http://www.fsc.gov.tw",monthsUrlList),monthsUrlList)

# gen url
dataDir <- "/home/gg/data/bankingCreditCard/"
fileName <- paste0(dataDir,fileName <- sub("&flag=doc$","",sub(".*file=/", "", monthsUrlList)))

# cal time
system.time(
  for (i in 1:length(fileName)){
    print(monthsUrlList[i])
    try(download.file(url = monthsUrlList[i], destfile = fileName[i], mode = "w"), silent = TRUE)
  }
)

# data size
sum((fileName %>% file.info)$size)
```




